The code and configuration files for this project are available on Github at \url{https://github.com/buckbaskin/animatlab}. In general, each section corresponds to a directory in the repository (the title links to the folder).

\bbs{\github{PuppyNeuronPlayground}}

This folder contains the Animatlab project used to test and design the synthetic nervous system controller. It includes a number of data tools for testing and development.

\bbs{\github{stability}}

This folder contains most of the Python simulation resources used for the project. It was originally named for its intention to measure and visualize the stability of controllers, but it also contains other work as well. Key files are \texttt{constant\_pressure.py}, \texttt{max\_torque.py}, \texttt{pressure\_torque.py}, \texttt{reduced\_controller.py}, \texttt{simple\_mass\_model.py}, \texttt{simulation.py}, and \texttt{torque\_projection.py}.

\bbs{\github{fitting\_neurons}}

This folder contains Python scripts used to fit the neuron model in \cite{NickFunctionalSubnetwork} to arithmetic operations.

\bbs{\github{testing}}

This folder was used to plan out testing setups for use in the controller tests.

\bbs{\github{writeup}}

This folder contains the materials used to create the full thesis writeup as well as a conference paper.

\bbss{\github{writeup/data}}

This subfolder contains the raw data exports from Animatlab as well as the Python script to convert the data to a more common \texttt{.csv} format and the converted CSV files.

\bbss{\github{writeup/scripts}}

This subfolder contains scripts used to more consistently visualize Animatlab data using \texttt{matplotlib}, a Python library.

\bbs{\github{Poster}}

This folder contains the materials used to create a poster for Case Western's Research Showcase.

\bbs{\github{ICanDoMath}}

This was a small Animatlab project used to verify the tuning of synapses in Python. Some of this functionality was ported to the main design project.

\bbs{\github{docs}}

This folder contains notes from eariler in the project.